
We can divide the probelm into two parts, $j=s$ and $j \neq s$.
\subsection{$j=s$}
    \begin{enumerate}
        \item \textbf{Lemma one: Algorithm to Find Subsets}
        Now, we have a set whose number of the element is $n$. Then we want to find out all the subsets whose 
        number of the element is $k$.\\
        \textbf{Algorithm: \\}
        \begin{itemize}
            \item First, we put the orign set to a container, and then we label every element to one(illustrate the picture below). 
            We assume that the orign set is $S$, $S=\{1,2,3,4,5\}$:\\
            \begin{table}[H]
            \centering
            \begin{tabular}{lllll}
            \hline
            \multicolumn{1}{|l|}{5} & \multicolumn{1}{l|}{4} & \multicolumn{1}{l|}{3} & \multicolumn{1}{l|}{2} & \multicolumn{1}{l|}{1} \\ \hline
            1                       & 1                      & 1                      & 1                      & 1                     
            \end{tabular}
            \end{table}
            Then, the subset which has the same element with the orignal set's, I'll label the element to 1, otherwise I'll label it to 0. For 
            example, we suppose that one the subset is $S_1$,$S_1=\{1,2,4\}$. We can represent it as below:\\
            \begin{table}[H]
            \centering
            \begin{tabular}{lllll}
            \hline
            \multicolumn{1}{|l|}{5} & \multicolumn{1}{l|}{4} & \multicolumn{1}{l|}{3} & \multicolumn{1}{l|}{2} & \multicolumn{1}{l|}{1} \\ \hline
            0                       & 1                      & 0                      & 1                      & 1                     
            \end{tabular}
            \end{table}
            Now we can change the number below the array to a binary number, which means that each subset can be represented by a unique number from 
            0(empty set) to $2^n-1$(orignal set). Just like the example above set $S$ can be represented by $11111_2 = 31_{10}$ and $S_1$ can be expressed 
            as $01011_2 = 11_{10}$
            \item Now, we know how to find subsets of the original set, but I want to know how to find the subset with the specific number of elements. 
            Therefore, we only need to know the subset whose binary number representation contains $k$ 1s. As the example above, $S_1=\{1,2,4\}$:
            \begin{table}[H]
            \centering
            \begin{tabular}{lllll}
            \hline
            \multicolumn{1}{|l|}{5} & \multicolumn{1}{l|}{4} & \multicolumn{1}{l|}{3} & \multicolumn{1}{l|}{2} & \multicolumn{1}{l|}{1} \\ \hline
            0                       & 1                      & 0                      & 1                      & 1                     
            \end{tabular}
            \end{table}
            So, the $S_1$ contains three elements, because it has three 1s.\\
            In this way, we can easily find out the subset whose number of elements is k from $0$ to $2^n-1$, the code illustrates below:
\begin{lstlisting}
void findSubsetOfk(int n,int k, vector<int> subsetK){
    int count=0;//number of 1s
    for(int i = 1 ; i < (1<<n); i++){
        for(int j = 0; j < n; j++){
            //the binary number representation 
            //of subset has an 1 on the jth position
            if(i & (1<<j)!=0){
                count++;
            }
        }
        if(count==k)
            susetK.empalce_back(i);
        count=0;
    }

}
\end{lstlisting}
        But,we can easily find that the binary number representation of the subset whose number of elements is k is 
        no less than $2^k-1$. Therefore, we the code above, we can have an optimization on the i. THe optimized code is 
        below:\\
\begin{lstlisting}
void findSubsetOfk(int n,int k, vector<int> subsetK){
    int count=0;//number of 1s
    for(int i = (1<<k)-1 ; i < (1<<n); i++){
        for(int j = 0; j < n; j++){
            //the binary number representation 
            //of subset has an 1 on the jth position
            if(i & (1<<j)!=0){
                count++;
            }
        }
        if(count==k)
            susetK.empalce_back(i);
        count=0;
    }

}
\end{lstlisting}
        \end{itemize}
        \begin{itemize}
            \item Currently, we can use the same way what we say above to find out the subset of the set whose number of element is 
            $k$ and its number of elements is $s$.
        \end{itemize}
    \item \textbf{Lemma two: Calculate the Combination number}\\
    If we calculate the combination number directly, it is likely to out of bounds of int. So we can use this combination formula below:
    $$C_n^m=C_{n-1}^{m-1}+C_{n-1}^m$$
    to calculate the combination number. The code is below:
\begin{lstlisting}
int calculateCombinationNumber(int n,int m){
    for(int i=0;i<=n;i++)
        C[i][0]=1;
    for(int i=1;i<=n;i++)
        for(int j=1;j<=i;j++)
            C[i][j]=C[i-1][j-1]+C[i-1][j];
    return C[n][m];
}
\end{lstlisting}
    \item \textbf{Lemma three: Greedy algorithm to calculate the set covergae}\\
    We denote that the input is a set $\mathcal{U}$ of n elements, and a collection $S=\{S_1, S_2, . . . , S_m\}$ of $m$ subsets of $\mathcal{U}$ such that
    $\cup_iS_i=\mathcal{U}$. Our goal is to take as few subsets as possible from $S$ such that their union covers $\mathcal{U}$.
    We can solve this problem easily by greedy algorithm. The algorithm is below:
    \begin{table}[H]
        \centering
        \begin{tabular}{|l|}
        \hline
        Greedy Cover($S$,$\mathcal{U}$)                                                     \\
        1. repeat                                                             \\
        2.     pick the set that covers the maximum number of uncover element \\
        3.     mark elements in the chosen set as covered                     \\
        4.     remove the set from $S$ to the result set                        \\
        5. done                                                               \\ \hline
        \end{tabular}
        \end{table}
    \end{enumerate}
    Based on the three lemmas above, we can easily transform the problem to that the set $\mathcal{U}=\{1,2,\cdots, C^j_n\}$, which means that we map each different subset 
    whose the number of the elements is j to a unique code from 1 to $ C^j_n$. Each subset of $S$, represents the each $k$ set's subsets whose number of elements is j. Ultimately, 
    we can solve the problem easily.
\subsection{$j \neq s$}
    The way to solve the problem is just like the way we mentioned above. However, after finishing finding the subset of the $k$ set whose element number is $s$, we should know how many sets 
    whose the number of elements is $j$ include it. Therefore, we use dfs(depth first search) to find out them.
    Assuming that $n=5, s=3, j=4$, and the subset whose number of elements is equal to 3 is labeled as $01011_2$. Therefore, we can expand it as below:
    \begin{table}[H]
        \centering
        \begin{tabular}{lllll}
        \hline
        \multicolumn{1}{|l|}{5} & \multicolumn{1}{l|}{4} & \multicolumn{1}{l|}{3} & \multicolumn{1}{l|}{2} & \multicolumn{1}{l|}{1} \\ \hline
        0                       & 1                      & 0                      & 1                      & 1                      \\
        0                       & 1                      & 1                      & 1                      & 1                      \\
        1                       & 1                      & 0                      & 1                      & 1                     
        \end{tabular}
        \end{table}
    Then, we should mark the last two rows of the set above in the $\mathcal{U}$ as covered.